Supplemental material

### 2024-09-03 manuscript_and_modelling_plots_takeovers.Rmd
edited figs and associated code

# regularising priors for parameter values
prior(student_t(5, 9, 2.5)) %>% 
  parse_dist() %>% 
  ggplot(aes(xdist = .dist_obj, y = prior)) + 
  stat_halfeye(.width = c(.5, .99)) +
  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
  scale_x_continuous(expression(italic(p)(beta[1]))) +
  theme_bw()

@@

# modelling average deceleration with regularising priors. Random effects structure is maximal. Distribution family is Gaussian.
mean_decel_gaussian_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                             dplyr::mutate(ppid = as.factor(ppid)),
                                           family = gaussian(),
                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                     prior(student_t(3, 0, 2.5), class = "b")),
                                           bf(mean_decel ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid)),
                                           control = list(adapt_delta = 0.99999999999),
                                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                           file = here::here("takeover_performance_cogload_time_budget/Models/mean_decel_gaussian_reg_priors_maximal"))
```

@@

# model of maximum longitudinal acceleration with priors
mean_lat_acc_lognormal_maximal <- brm(data = response.vehicle.eye %>%
                                        dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                        dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                        dplyr::mutate(ppid = as.factor(ppid)),
                                      family = lognormal(),
                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                prior(student_t(3, 0, 2.5), class = "b")),
                                       bf(mean_lat_acc ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid)),
                                      control = list(adapt_delta = 0.99999999999),
                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                      file = here::here("takeover_performance_cogload_time_budget/Models/mean_lat_acc_lognormal_maximal"))

pp_check(mean_lat_acc_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
pp_check(mean_lat_acc_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")

pp_check(mean_lat_acc_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
pp_check(mean_lat_acc_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
```

@@

# initial model of SDLP
sdlp_lognormal_maximal <- brm(data = response.vehicle.eye %>%
                                dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
                                dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                dplyr::mutate(ppid = as.factor(ppid)),
                              family = lognormal(),
                              prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                        prior(student_t(3, 0, 2.5), class = "b")),
                              bf(sdlp ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
                                   control = list(adapt_delta = 0.95),
                                   iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
                                   file = here::here("takeover_performance_cogload_time_budget/Models/sdlp_lognormal_maximal"))

pp_check(sdlp_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
pp_check(sdlp_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")

pp_check(sdlp_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
pp_check(sdlp_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

pp_check(sdlp_lognormal_maximal, type = "hist", group = "ttc_criticality_factor")
```

@@

sd_yaw_automation_lognormal_maximal <- brm(data = response.vehicle.eye %>%
                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                             dplyr::mutate(ppid = as.factor(ppid)),
                           family = lognormal(),
                           sd_yaw_automation ~ n_back + (n_back | ppid),
                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                     prior(student_t(3, 0, 2.5), class = "b")),
                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
                                                   file = here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_automation_lognormal_maximal"))

@@

```{r}
# model summmary
print(summary(sd_yaw_automation_gaussian_maximal), digits = 5)
describe_posterior(sd_yaw_automation_gaussian_maximal, centrality = "mean")

# average predicted SD of yaw during automation with and without n-back
predicted_sd_yaw_automation_nback <- sd_yaw_automation_gaussian_maximal %>% 
  epred_draws(newdata = expand_grid(n_back = c(TRUE, FALSE)),
              re_formula = NA)

# average marginal effect of n-back
sd_yaw_automation_MER_nback <- sd_yaw_automation_gaussian_maximal %>% 
  emmeans(~ n_back,
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

sd_yaw_automation_MER_nback  %>% mean_hdi()

## Log normal model summary

@@

sd_yaw_manual_trunc_gaussian_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_trunc_gaussian_maximal.rds"))

# initial model of sd_yaw
sd_yaw_manual_trunc_gaussian_maximal <- brm(data = response.vehicle.eye %>%
                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                             dplyr::mutate(ppid = as.factor(ppid)),
                           family = gaussian(),
                           bf(sd_yaw_manual | trunc(lb = 0) ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                     prior(student_t(3, 0, 2.5), class = "b")),
                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
                           control = list(adapt_delta = 0.95),
                           file = here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_trunc_gaussian_maximal"))

# posterior predictive checks
pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "n_back")

pp_check(sd_yaw_manual_gaussian_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
pp_check(sd_yaw_manual_gaussian_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

# posterior predictive checks
pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
pp_check(sd_yaw_manual_gaussian_maximal, type = "stat_grouped", stat = "mean", group = "n_back")

pp_check(sd_yaw_manual_trunc_gaussian_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100)
pp_check(sd_yaw_manual_trunc_gaussian_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)
```

@@

#### predicted posterior means and distribution ####
predicted_draws = empty_grid %>%
  add_predicted_draws(sd_yaw_manual_gaussian_maximal)

expected_values = empty_grid %>%
  add_epred_draws(sd_yaw_manual_gaussian_maximal)

@@

```{r}
# relative size of  heterogenity effect for 2-back on mu
summary(sd_yaw_manual_gaussian_maximal)[["random"]][["ppid"]][2,1] / summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1]

@@

# individual effects for SD of yaw during manual driving
ppid.effects <- as.data.frame(ranef(sd_yaw_manual_gaussian_maximal)) %>%
  dplyr::select(ppid.Estimate.n_backTRUE) %>%
  dplyr::mutate(ranef = ppid.Estimate.n_backTRUE + summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1]) %>%
  tibble::rownames_to_column("ppid")

@@

# CI interval for average effect
bayes.credible.intervals <- as.data.frame(summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][3:4])

# select random effects parameter 
ran.effects <- summary(sd_yaw_manual_gaussian_maximal)[["random"]][["ppid"]][2,1]

# strip plot of individual effects
strip_plot <- ggplot() +
  geom_jitter(ppid.effects, mapping = aes(x = x, y = ranef), width = .05, height = 0, size = 4,
              shape = 21, colour = "black", fill = viridis(5)[3], alpha = .95, stroke = 1) +
  scale_y_continuous(limits = c(-4.5, 3), breaks = seq(-4.5, 3, 1.5), labels = label_number(accuracy = 0.1)) +
  ylab(expression("N-back effect on" ~ mu ~ "of" ~ SD[YAW] ~ "during manual driving (°)")) +
  xlab("") + 
  ggtitle("A") +
  xlim(-1, 1) +
  geom_hline(aes(yintercept = bayes.credible.intervals$`l-95% CI`[2], linetype ="95% CI"), size = 1.5,  color = viridis(5)[3]) +
  geom_hline(aes(yintercept = bayes.credible.intervals$`u-95% CI`[2], linetype="95% CI"), size = 1.5,  color = viridis(5)[3]) +
  geom_hline(aes(yintercept = summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1], linetype = "beta_1"), size = 1.5, color = "black") +
  geom_hline(aes(yintercept = summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1] + 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
  geom_hline(aes(yintercept = summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1] - 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
  scale_linetype_manual(name = " ", values = c(2, 1, 1), labels = c(expression(CI[95]), expression(HI[95]), expression(beta[N])), guide = guide_legend(override.aes = list(color = c(viridis(5)[3], viridis(5)[2], "black")))) +
  scale_fill_manual(name = "Parameter", values = c(viridis(5)[2])) +
   annotate( # increased gaze concentration
    'rect',
    xmin = -.25,
    xmax = .25,
    ymin = -2.49,
    ymax = -2.24,
    alpha = 0.5, # This was put back to 0.5
    fill = turbo(5)[5],
    col = 'black'
  ) +
  annotate( # no difference in gaze concentration
    'rect',
    xmin = -.25,
    xmax = .25,
    ymin = -.1,
    ymax = .15,
    alpha = 0.5, # This was put back to 0.5
    fill = viridis(5)[4],
    col = 'black'
  ) +
  theme_bw() +
  coord_flip() + 
  theme(legend.position = c(.181, .60), panel.grid.major.y = element_blank(), panel.grid.minor.y = element_blank(),legend.key = element_blank(), legend.key.width = unit(0.2, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.key.size = unit(.05, 'cm'), plot.title = element_text(size = 15, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 7))

# heterogenity intervals for the effect of N-back on SD of yaw during manual driving
summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1] + 1.96 * ran.effects
summary(sd_yaw_manual_gaussian_maximal)[["fixed"]][2,1] - 1.96 * ran.effects

# participant 3, beta_n = -0.065
p_3 <- ggplot(dat.eye.manual %>%
         dplyr::filter(ppid == 3), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  scale_colour_viridis_c(option = "C") +
  ggtitle(label = "B",
          subtitle = "Participant 3," ~ beta[N[3]] ~ "= -.065") +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        strip.text = element_text(face = "bold", size = 10),
        plot.subtitle = element_text(size = 12, colour = viridis(5)[4]),
        plot.title = element_text(size = 15, face = "bold"))

# participant 14, beta_n = .036
p_14 <- ggplot(dat.eye.manual %>%
         dplyr::filter(ppid == 14), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  scale_colour_viridis_c(option = "C") +
  ggtitle(label = " ",
          subtitle = "Participant 14," ~ beta[N[14]] ~ "= .036") +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        strip.text = element_text(face = "bold", size = 10),
        plot.subtitle = element_text(size = 12, colour = viridis(5)[4]),
        plot.title = element_text(size = 15, face = "bold"))

# participant 7, beta_n = -2.128
p_7 <- ggplot(dat.eye.manual %>%
         dplyr::filter(ppid == 7), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  scale_colour_viridis_c(option = "C") +
  ggtitle(label = "C",
          subtitle = "Participant 7," ~ beta[N[7]] ~ "= -2.128") +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        strip.text = element_text(face = "bold", size = 10),
        plot.subtitle = element_text(size = 12, colour = turbo(5)[5]),
        plot.title = element_text(size = 15, face = "bold"))

# participant 13, beta_n = -2.391
p_13 <- ggplot(dat.eye.manual %>%
         dplyr::filter(ppid == 13), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  scale_colour_viridis_c(option = "C") +
  ggtitle(label = " ",
          subtitle = "Participant 13," ~ beta[N[13]] ~ "= -2.391") +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        strip.text = element_text(face = "bold", size = 10),
        plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 12, colour = turbo(5)[5]))

>>>>

# regularising priors for parameter values
prior(normal(0, 5)) %>% 
  parse_dist() %>% 
  ggplot(aes(xdist = .dist_obj, y = prior)) + 
  stat_halfeye(.width = c(.5, .99)) +
  scale_y_discrete(NULL, breaks = NULL, expand = expansion(add = 0.1)) +
  scale_x_continuous(expression(italic(p)(beta[1]))) +
  theme_bw()

@@

# modelling average deceleration with regularising priors. Random effects structure is maximal. Distribution family is Gaussian.
mean_decel_gaussian_reg_priors_maximal <- brm(data = response.vehicle.eye %>%
                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                             dplyr::mutate(ppid = as.factor(ppid)),
                                           family = gaussian(),
                                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                     prior(student_t(3, 0, 2.5), class = "b")),
                                           bf(mean_decel ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid)),
                                           control = list(adapt_delta = 0.99999999999),
                                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                           file = here::here("takeover_performance_cogload_time_budget/Models/mean_decel_gaussian_reg_priors_maximal"))

print(summary(mean_decel_skewnormal_reg_priors_maximal), digits = 5)
describe_posterior(mean_decel_skewnormal_reg_priors_maximal, centrality = "mean")
```

@@

# model of maximum longitudinal acceleration with priors
mean_lat_acc_lognormal_maximal <- brm(data = response.vehicle.eye %>%
                                        dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, ho.rt > .15, collision == 0) %>%
                                        dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                        dplyr::mutate(ppid = as.factor(ppid)),
                                      family = lognormal(),
                                      prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                                prior(student_t(3, 0, 2.5), class = "b")),
                                       bf(mean_lat_acc ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor | ppid)),
                                      control = list(adapt_delta = 0.99999999999),
                                      iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13,
                                      file = here::here("takeover_performance_cogload_time_budget/Models/mean_lat_acc_lognormal_maximal"))
```

@@

# initial model of SDLP
sdlp_lognormal_maximal <- brm(data = response.vehicle.eye %>%
                                dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
                                dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                                dplyr::mutate(ppid = as.factor(ppid)),
                              family = lognormal(),
                              prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                        prior(student_t(3, 0, 2.5), class = "b")),
                              bf(sdlp ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
                                   control = list(adapt_delta = 0.95),
                                   iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
                                   file = here::here("takeover_performance_cogload_time_budget/Models/sdlp_lognormal_maximal"))
```

@@

sd_yaw_automation_lognormal_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_automation_lognormal_maximal.rds"))

sd_yaw_automation_lognormal_maximal <- brm(data = response.vehicle.eye %>%
                                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                             dplyr::mutate(ppid = as.factor(ppid)),
                           family = lognormal(),
                           sd_yaw_automation ~ n_back + (n_back | ppid),
                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                     prior(student_t(3, 0, 2.5), class = "b")),
                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
                                                   file = here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_automation_lognormal_maximal"))
```

@@

```{r}
## Log normal model summary

@@

# truncated Gaussian model
sd_yaw_manual_trunc_gaussian_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_trunc_gaussian_maximal.rds"))

sd_yaw_manual_trunc_gaussian_maximal <- brm(data = response.vehicle.eye %>%
                             dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
                             dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x)) %>%
                             dplyr::mutate(ppid = as.factor(ppid)),
                           family = gaussian(),
                           bf(sd_yaw_manual | trunc(lb = 0) ~ n_back * ttc_criticality_factor + (n_back * ttc_criticality_factor| ppid)),
                           prior = c(prior(student_t(3, 0, 2.5), class = "Intercept"),
                                     prior(student_t(3, 0, 2.5), class = "b")),
                           iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13, 
                           control = list(adapt_delta = 0.95),
                           file = here::here("takeover_performance_cogload_time_budget/Models/sd_yaw_manual_trunc_gaussian_maximal"))
```

@@

#### predicted posterior means and distribution ####
predicted_draws = empty_grid %>%
  add_predicted_draws(sd_yaw_manual_trunc_gaussian_maximal)

expected_values = empty_grid %>%
  add_epred_draws(sd_yaw_manual_trunc_gaussian_maximal)

@@

```{r}
# relative size of  heterogenity effect for 2-back on mu
summary(sd_yaw_manual_trunc_gaussian_maximal)[["random"]][["ppid"]][2,1] / summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1]

@@

# individual effects for SD of yaw during manual driving
ppid.effects <- as.data.frame(ranef(sd_yaw_manual_trunc_gaussian_maximal)) %>%
  dplyr::select(ppid.Estimate.n_backTRUE) %>%
  dplyr::mutate(ranef = ppid.Estimate.n_backTRUE + summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1]) %>%
  tibble::rownames_to_column("ppid")

@@

# CI interval for average effect
bayes.credible.intervals <- as.data.frame(summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][3:4])

# select random effects parameter 
ran.effects <- summary(sd_yaw_manual_trunc_gaussian_maximal)[["random"]][["ppid"]][2,1]

# strip plot of individual effects
strip_plot <- ggplot() +
  geom_jitter(ppid.effects, mapping = aes(x = x, y = ranef), width = .05, height = 0, size = 4,
              shape = 21, colour = "black", fill = viridis(5)[3], alpha = .95, stroke = 1) +
  scale_y_continuous(limits = c(-4.5, 3), breaks = seq(-4.5, 3, 1.5), labels = label_number(accuracy = 0.1)) +
  ylab(expression("N-back effect on" ~ mu ~ "of" ~ SD[YAW] ~ "during manual driving (°)")) +
  xlab("") + 
  ggtitle("A") +
  xlim(-1, 1) +
  geom_hline(aes(yintercept = bayes.credible.intervals$`l-95% CI`[2], linetype ="95% CI"), size = 1.5,  color = viridis(5)[3]) +
  geom_hline(aes(yintercept = bayes.credible.intervals$`u-95% CI`[2], linetype="95% CI"), size = 1.5,  color = viridis(5)[3]) +
  geom_hline(aes(yintercept = summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1], linetype = "beta_1"), size = 1.5, color = "black") +
  geom_hline(aes(yintercept = summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1] + 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
  geom_hline(aes(yintercept = summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1] - 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
  scale_linetype_manual(name = " ", values = c(2, 1, 1), labels = c(expression(CI[95]), expression(HI[95]), expression(beta[N])), guide = guide_legend(override.aes = list(color = c(viridis(5)[3], viridis(5)[2], "black")))) +
  scale_fill_manual(name = "Parameter", values = c(viridis(5)[2])) +
   annotate( # increased gaze concentration
    'rect',
    xmin = -.25,
    xmax = .25,
    ymin = -2.49,
    ymax = -2.24,
    alpha = 0.5, # This was put back to 0.5
    fill = turbo(5)[5],
    col = 'black'
  ) +
  annotate( # no difference in gaze concentration
    'rect',
    xmin = -.25,
    xmax = .25,
    ymin = -.1,
    ymax = .15,
    alpha = 0.5, # This was put back to 0.5
    fill = viridis(5)[4],
    col = 'black'
  ) +
  theme_bw() +
  coord_flip() + 
  theme(legend.position = c(.181, .60), panel.grid.major.y = element_blank(), panel.grid.minor.y = element_blank(),legend.key = element_blank(), legend.key.width = unit(0.2, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.key.size = unit(.05, 'cm'), plot.title = element_text(size = 15, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 7))

# heterogenity intervals for the effect of N-back on SD of yaw during manual driving
summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1] + 1.96 * ran.effects
summary(sd_yaw_manual_trunc_gaussian_maximal)[["fixed"]][2,1] - 1.96 * ran.effects

# participant 3, beta_n = -0.022
p_3 <- ggplot(dat.eye.manual %>%
         dplyr::filter(ppid == 3), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  scale_colour_viridis_c(option = "C") +
  ggtitle(label = "B",
          subtitle = "Participant 3," ~ beta[N[3]] ~ "= -.022") +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        strip.text = element_text(face = "bold", size = 10),
        plot.subtitle = element_text(size = 12, colour = viridis(5)[4]),
        plot.title = element_text(size = 15, face = "bold"))

# participant 14, beta_n = 0.052
p_14 <- ggplot(dat.eye.manual %>%
         dplyr::filter(ppid == 14), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  scale_colour_viridis_c(option = "C") +
  ggtitle(label = " ",
          subtitle = "Participant 14," ~ beta[N[14]] ~ "= .052") +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        strip.text = element_text(face = "bold", size = 10),
        plot.subtitle = element_text(size = 12, colour = viridis(5)[4]),
        plot.title = element_text(size = 15, face = "bold"))

# participant 7, beta_n = -2.424
p_7 <- ggplot(dat.eye.manual %>%
         dplyr::filter(ppid == 7), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  scale_colour_viridis_c(option = "C") +
  ggtitle(label = "C",
          subtitle = "Participant 7," ~ beta[N[7]] ~ "= -2.424") +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        strip.text = element_text(face = "bold", size = 10),
        plot.subtitle = element_text(size = 12, colour = turbo(5)[5]),
        plot.title = element_text(size = 15, face = "bold"))

# participant 13, beta_n = -2.317
p_13 <- ggplot(dat.eye.manual %>%
         dplyr::filter(ppid == 13), mapping = aes(x = yaw, y = pitch)) +
  geom_density_2d(aes(col = ..level..), alpha = .5, binwidth = .00003) +
  facet_wrap(~ n_back, labeller = labeller(n_back = l.labs)) +
  scale_colour_viridis_c(option = "C") +
  ggtitle(label = " ",
          subtitle = "Participant 13," ~ beta[N[13]] ~ "= -2.317") +
  xlab("Yaw (°)") +
  ylab("Pitch (°)") +
  xlim(-50, 50) +
  scale_y_continuous(limits = c(-32, 20), breaks = seq(-30, 20, 15)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 11), 
        axis.text.x = element_text(size = 11), 
        axis.title.y = element_text(size = 11), 
        axis.text.y = element_text(size = 11), 
        title = element_text(size = 18),
        strip.text = element_text(face = "bold", size = 10),
        plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 12, colour = turbo(5)[5]))

### 2024-09-03 supplemental_material.Rmd
edited figs and associated code

if(!require(ggforce)) install.packages("ggforce")
library(ggforce)
```

@@

>>>>

if(!require(ggforce)) install.packages("ggforce")
library(ggforce)

if(!require(afex)) install.packages("afex")
library(afex)

if(!require(BayesFactor)) install.packages("BayesFactor")
library(BayesFactor)
```

@@

## Identifying order effects

```{r}
# braking reaction time
rt_order <- anovaBF(rt ~ event.order.factor, data = response.vehicle.eye %>% 
                      dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
                      dplyr::group_by(ppid, event.order.factor) %>%
                      dplyr::summarise(rt = mean(rt)))

rt_order

# hands on time
hort_order <- anovaBF(ho.rt ~ event.order.factor, data = response.vehicle.eye %>%
                        dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
                        dplyr::group_by(ppid, event.order.factor) %>%
                        dplyr::summarise(ho.rt = mean(ho.rt)))

hort_order

# mean decel
decel_order <- anovaBF(mean_decel ~ event.order.factor, data = response.vehicle.eye %>%
                         dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
                         dplyr::group_by(ppid, event.order.factor) %>%
                          dplyr::summarise(mean_decel = mean(mean_decel)))

decel_order

# mean lateral accelerations
lat_order <- anovaBF(mean_lat_acc ~ event.order.factor, data = response.vehicle.eye %>%
                       dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
                       dplyr::group_by(ppid, event.order.factor) %>%
                        dplyr::summarise(mean_lat_acc = mean(mean_lat_acc)))

lat_order

# sdlp
sdlp_order <- anovaBF(sdlp ~ event.order.factor, data = response.vehicle.eye %>%
                        dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
                        dplyr::group_by(ppid, event.order.factor) %>%
                        dplyr::summarise(sdlp = mean(sdlp))
                        )

sdlp_order

# SD of yaw - automation
yaw_automation <- anovaBF(sd_yaw_automation ~ event.order.factor, data = response.vehicle.eye %>%
                        dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
                        dplyr::group_by(ppid, event.order.factor) %>%
                        dplyr::summarise(sd_yaw_automation = mean(sd_yaw_automation))
                        )

yaw_automation

# SD of yaw - manual
yaw_manual <- anovaBF(sd_yaw_manual ~ event.order.factor, data = response.vehicle.eye %>%
                        dplyr::mutate(event.order.factor = as.factor(event.order)) %>%
                        dplyr::group_by(ppid, event.order.factor) %>%
                        dplyr::summarise(sd_yaw_manual = mean(sd_yaw_manual))
                        )

yaw_manual
```
